\documentclass[letterpaper,notitlepage,twoside]{article}

% Basic imports, increase margins...
\usepackage[margin=0.75in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}

% Finite State Machine stuff
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

% Format tables nicely
\usepackage[latin1]{inputenc}
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}

\usepackage{amsfonts} 
\usepackage{amssymb}
\usepackage{amsmath,amsthm}

\renewcommand{\implies}{\Rightarrow} % redefine command "implies"  
\renewcommand{\iff}{\Leftrightarrow} % double arrow
\newcommand{\maps}{\rightarrow} % define command "map" 
\newcommand{\union}{\cup}
\newcommand{\intersect}{\cap}
\newcommand{\N}{\mathbb{N}} % natural number 
\newcommand{\Q}{\mathbb{Q}} % rational number 
\newcommand{\R}{\mathbb{R}} % real number 
\newcommand{\Z}{\mathbb{Z}} % integers 
\newcommand\tab[1][1cm]{\hspace*{#1}} %\tab command

% Add more packages that you use here...

\begin{document}
\title{Homework 15}
\author{Joe Baker, Brett Schreiber, Brian Knotten}
\maketitle

\section*{23}
Problem 6.3 Describe a decidable language in $P/_{poly}$ that is not in $P$
\\\\
From the Time Hierarchy Theorem we know there exists a decidable language $L \notin EXP$. Using $L$, we can construct the unary language $L' = \{1^{n} | n \in L\}$. Clearly, by the proof of claim 6.8 in the book, $L' \in P/_{poly}$. To show that $L' \notin P$, assume the opposite: therefore $\exists$ TM $M$ that decides $L'$ in time $O(n^{k})$. We could then use $M$ to construct the TM $M'$ that decides $L$ in time $O((2^{n})^{k})$, meaning that $L \in EXP$ - a contradiction. All that remains is to show that $L'$ is decidable; this is trivial however, as $L$ is decidable so we merely define $L'$ to reject all inputs not of the form $1^{n}$ and accept only if $n \in L$. Therefore $\exists$ decidable language $L'$ such that $L' \in P_{poly}$ and $L' \notin P$.

\section*{24}

\subsection*{a}
Problem 6.5: Show for every $k > 0$ that PH contains languages whose circuit complexity is $\Omega\left(n^k\right)$.
\\\\
Proof:
\\
Let $C$ be a circuit with complexity at of at least $n^k$. We know that such a circuit must exist by Theorem 6.22 from the book. We can construct a boolean formula $F$ from the gates of $C$ with $k$ quantifiers over the boolean formula. Now let $L$ be the language of all variable assignments for $k$ which satisfy $F$. Since $\left| C \right|$ is polynomial, $C$ can decide if an input is valid for $F$ in polynomial time. So there must exist a TM $M$ with $k$ advice tapes (from the quantifiers) that can decide the input with its advice tapes in polynomial time. Thus for each $k > 0$, there is a language in PH whose circuit complexity is $\Omega\left(n^k\right)$.

\subsection*{b}
Problem 6.6: Show for every $k > 0$ that $\Sigma_2^p$ contains languages whose circuit complexity is $\Omega\left(n^k\right)$.
\\\\
Proof:
\\
Consider the circuit $C$ from problem 6.5. Now construct the same formula $F$, but only use two quantifiers. One $\exists$ over the tuple of some of the variables and one $\forall$ for the remaining tuple of variables. Again let $L$ be the language of all variable assignments for $k$ which satisfy $F$. Since $\left| C \right|$ is polynomial, $C$ can decide if an input is valid for $F$ in polynomial time. So there must exist a TM $M$ with 2 advice tapes (from the quantifiers) that can decide the input with its advice tapes in polynomial time. Thus for each $k > 0$, there is a language in $\Sigma_2^p$ whose circuit complexity is $\Omega\left(n^k\right)$.

\subsection*{c}
Problem 6.7: Show that if P = NP, then there is a language in EXP that requires circuits of size $\frac{2^n}{n}$.
\\\\
Proof:
\\
Assume P = NP and let $L \in $ EXP. If $L$ is decidable by a circuit of complexity $n^k$, then because the polynomial hierarchy is collapsible and by problem 6.6, $L$ is in P. So any $L$ in EXP that is not in P must have a circuit with complexity $\frac{2^n}{n}$.

\end{document}
