\documentclass[letterpaper,notitlepage,twoside]{article}

% Basic imports, increase margins...
\usepackage[margin=0.75in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}

% Finite State Machine stuff
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

% Format tables nicely
\usepackage[latin1]{inputenc}
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}

\usepackage{amsfonts} 
\usepackage{amssymb}
\usepackage{amsmath,amsthm}

\renewcommand{\implies}{\Rightarrow} % redefine command "implies"  
\renewcommand{\iff}{\Leftrightarrow} % double arrow
\newcommand{\maps}{\rightarrow} % define command "map" 
\newcommand{\union}{\cup}
\newcommand{\intersect}{\cap}
\newcommand{\N}{\mathbb{N}} % natural number 
\newcommand{\Q}{\mathbb{Q}} % rational number 
\newcommand{\R}{\mathbb{R}} % real number 
\newcommand{\Z}{\mathbb{Z}} % integers 
\newcommand\tab[1][1cm]{\hspace*{#1}} %\tab command

\begin{document}
\title{Homework N}
\author{Joe Baker, Brett Schreiber, Brian Knotten}
\maketitle

\section*{11}
\begin{itemize}

\item Show that the set of semi-incompressible strings is not computable. \\
Assume that the set of semi-incompressible strings is computable to reach a contradiction. \\
Therefore $\exists$ TM $M$ the computes the set of semi-incompressible strings. \\
Consider the TM $N$ that for each string $x$ of size $n$: \\
\tab If $M$ halts on $x$, print $x$ and halt. \\
$|N| = O(log_{2} n)$, which is $< \sqrt{n}$ for a sufficiently large $n$, contradicting the semi-incompressibility of $x$.\\

\item Show that the set of compressible strings is recursively enumerable.\\
A string is compressible if it is not incompressible.\\
The set of all strings is enumerable. Consider each string to be an integer of base $|\Gamma|$ where $|\Gamma|$ is the size of the alphabet. \\
For an alphabet $\Gamma = \{0, 1\}$, then $ALL\_STRINGS = \{\epsilon, 0, 1, 00, 01, 10, 11, 000, 001,...\}$
Consider the TM $M$ which: \\
For each string $s$ in $ALL\_STRINGS$: \\
	\tab for each string $t$ in $ALL\_STRINGS$ where $|t| < |s|$ \\
		\tab\tab if $t$ describes $s$, output $s$ and break to outer for loop \\		
Since $|t|$ is less than $|s|$, and $t$ perfectly describes $s$, then $t$ is a compressed version of $s$. Therefore, $s$ is compressible. Since $M$ checks all strings which are less than the given string $s$, then $M$ will eventually find a compressed version of $s$ if it exists. Therefore $L(M)$, the set of compressible strings, is recursively enumerable.


\end{itemize}
\section*{12}

\end{document}