\documentclass[letterpaper,notitlepage,twoside]{article}

% Basic imports, increase margins...
\usepackage[margin=0.75in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}

% Finite State Machine stuff
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

% Format tables nicely
\usepackage[latin1]{inputenc}
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}

\usepackage{amsfonts} 
\usepackage{amssymb}
\usepackage{amsmath,amsthm}

\renewcommand{\implies}{\Rightarrow} % redefine command "implies"  
\renewcommand{\iff}{\Leftrightarrow} % double arrow
\newcommand{\maps}{\rightarrow} % define command "map" 
\newcommand{\union}{\cup}
\newcommand{\intersect}{\cap}
\newcommand{\N}{\mathbb{N}} % natural number 
\newcommand{\Q}{\mathbb{Q}} % rational number 
\newcommand{\R}{\mathbb{R}} % real number 
\newcommand{\Z}{\mathbb{Z}} % integers 
\newcommand\tab[1][1cm]{\hspace*{#1}} %\tab command

% Add more packages that you use here...

\begin{document}
\title{Homework 9}
\author{Joe Baker, Brett Schreiber, Brian Knotten}
\maketitle

\section*{13}
Definition 1:  $TIME(T(n))$ is the set of all languages $L$ such that $\exists$ TM $M$ such that (1) $M$ accepts $x$ iff $x \in L$ and (2) $\forall$ but finitely many $x$, $M$ on $x$ halts in $T(|x|)$ steps. \\
Definition 2: $TIME(T(n))$ is the set of all languages $L$ such that $\exists$ TM $N$ and a number $b$ such that (1) $N$ accepts $x$ iff $x \in L$ and (2) $\forall x$, $N$ on $x$ halts within $b * T(|x|)$ steps. \\ \\
First, show $M \implies N$: \\
Given $M$, there exists a finite number of strings $X$ such that $M$ does not halt on each $x \in X$ in $T(|x|)$ steps. \\
Consider the running time of $M$ on each $x_i \in X$. Let $s_i$ be the number of steps $M$ takes to accept $x_i$.\\
Let $b_i = \frac{s_i}{|x_i|}$. Therefore $s_i = b_i * |x_i|$.\\
Let $b$ be the largest $b_i$ for all $x_i \in X$.\\
Now construct $N$ as a Turing machine which does the following: \\
On input $x$: \\
	\tab Run $M$ on $x$ while counting the number of steps. \\
	\tab If $M$ accepts $x$ in $b * T(|x|)$ steps, then accept. \\
$N \in TIME(T(n))$ because it accepts $x$ within some number $b * T(|x|)$ steps. Therefore $M \implies N$. \\ \\
Second, show $N \implies M:$ \\
We will use $N$ that accepts $x$ in $b * T(|x|)$ steps to build $M$ that accepts $x$ in $T(|x|)$ steps with finitely many exceptions. \\
Given $N$, we will construct $M$'s alphabet $\gamma '$ and set of states $Q'$ from $N$'s alphabet $\gamma$ and set of states $Q$ as follows: \\
$\gamma ' = \gamma \cup \gamma^{b}$ \\
$Q'$ = $Q \times b \times \gamma^{3b} \cup Q \times \gamma^{i}$ where $i = 1, ..., m-1$ \\
Define $M$ as follows:
\begin{itemize}
\item Copy the input from the read tape to a new tape in chunks of size $b$ using the symbols from $\gamma'$ that correspond to the chunks. 
\item As each symbol in a chunk of $b$ is read $M$ will transition to a new state in $Q \times \gamma^{i}$ in order to remember the symbols in the chunk it has read. 
\item When the end of the input is encountered, pad the rest of the chunk with spaces until the chunk has size $b$ 
\item$M$ will then perform four steps by moving to the left once, right twice, and to the left once again. During each of these steps $M$ will move to a state in $Q \times b \times \gamma^{3b}$ to track the next $b$ steps of $N$. 
\item When $M$ encounters an accepting state of $N$, accept.
\end{itemize}
$M$ executes every $b$ number of steps of $N$ in a constant number of steps, so $M$ runs in $T(|x|)$ time and accepts iff $N$ accepts. \\ \\
We have shown that given $M$ we can construct $N$ and therefore $M \implies N$ and that given $N$ we can construct $M$ and therefore $N \implies M$. Thus, $M \Leftrightarrow N$ and the definitions are equivalent.




\end{document}